Cyclone: Fault Tolerance Middleware for NVM Clusters

### 2016-02-16 paper/paper.tex
paper updates

\subsection{Synchronous Replication}

\section{Multi-node Programming Model}

\subsection{Example: Distributed Transactions}

>>>>

\subsection{Synchronous Replication}
Asynchronous replication provides good performance but lacks some guarantees
necessary for certain distributed systems paradigms such as output commit and
the ability to integrate code that has non-deterministic execution paths or side
effects - such as reading the time. Cyclone therefore provides programmers the
ability to closely synchronize execution across the replicas using synchronous
replication. Synchronous replication extends the programming model provided by
cyclone to users - neccessitating some awareness on the part of the user about
the difference between the leader and follower replicas. We show later
(Sec~\ref{sec:examples}) how this awareness enables the crafting of efficient
fault tolerant application with little effort on the part of the programmer.

Figure~\ref{fig:sync_rep} shows how synchronous replication operates. Execution
of the RPC call is only initiated when the call and its arguments have been
replicated. This ensures that any side effects such as calls to other machines
only happen after it is guaranteed that the effects of the RPC call will be
committed to the replicas. This provides the output commit property necessary
for some of the applications we discuss below. Next the RPC call is executed on
the leader and the result of the RPC call is replicated to the followers. The
followers then proceed to execute the RPC call locally taking into account the
result from the leader. This result can include data to synchronize
non-deterministic steps such as reading the time on the replica. This process is
always conditional on the view (current configuration of replicas and choice
leader) staying unchanged. On a view change the process is reexcuted to ensure
than only one set of RPC call results is propagated across the replicas.

\begin{figure}
{\scriptsize
\begin{verbatim}
Initiate replication of RPC call and arguments
TX_BEGIN {
  while(!replication_complete);
  if(replication_failed) {
    TX_ABORT;
  }  
  while(true) {
    if(is_leader && !have_execution_result) {
      Execute RPC call and modify local NVM
      replicate_rpc_call_result in current view;
      if(result replication failed) {
        continue;
      }
      while(!result replication complete && !view change);
      if(view change) {
        continue;
      }
    }
    else {
      while(!result replication complete && !view change);
      if(view change) {
        continue;
      }
      Execute RPC call to modify local NVM with result from leader
    }
  }
} TX_END
\end{verbatim}
}
\caption{Synchronous Replication}
\label{fig:sync_rep}
\end{figure}

\section{Example Applications}
